% !TeX root = ../main.tex
% Add the above to each chapter to make compiling the PDF easier in some editors.

\chapter{Motivation}\label{chapter:motivation}

In this section we will lay down the main reasons to use a meal plan generated grocery shopping list. First we will show the efficiency of using a shopping list in general. Later we will take a look at physiological and psychological benefits of using a meal plan. \\
%Shopping list efficiency

After housing, food is the second largest expense of an average household. Grocery shopping takes up over an hour per week. Shopping lists can help to organize this process and to reduce the amount of time aswell as money spend in a store.
Women are more likely to use a shopping list: 69\% of women are using lists compared to 52\% of men. The majority of shopping lists are paper-based. Only 3\% of shoppers use a digital list. Digital shopping lists are easier to maintain. 
In most of shopping list apps, items can simply be ticked off, or altered otherwise. For households with multiple people shopping groceries, synchronisation can be done quite easily. This can lead to less redundant purchases and less waste. A very simple feature, that helps organizing a shopping list is the categorisation of items on the list. This is another benefit over paper-based lists, on which you cant rearrange items. A good categorisation - that is similar to the organisation in the store - allows us to save a lot of time and searching while grocery shopping.
We will show optimisation of categorisation in ~\ref{section:categorisation} \\

%Health issues

%The metabolic syndrom is a metabolic disorder, causing a increased risk of coronary heart diseases, heart attacks aswell as type 2 diabetes. It is caused by high blood sugar, blood preasure and high levels of triglycerides aswell as low levels of HDL cholosterol in the blood.

Data from the AHA showed metabolic syondrome or syndrome X for 35.5\% of adults in the USA in 2012, with numbers expected to have risen since then. There are links between metabolic syndrom and diet.Furthermore studies have shown, that a diet following a meal plan can help people with loosing weight. In conclusion weight reduction is a key element in the prevention and treatment of the metabolic syndrom.
The metabolic syndrom is a metabolic disorder, causing an increased risk of coronary heart diseases, heart attacks aswell as type 2 diabetes. It is caused by high blood sugar, blood preasure and high levels of triglycerides aswell as low levels of HDL cholesterol. The data showed metabolic syndrome or syndrome X for 35.5\% of adults in the USA in 2012, with numbers having risens since ~\parencite{hirode2020trends}.
[todo: mealplan verknüpfung]
 There are links between metabolic syndrom and diet, and studies have shown that a diet following a meal plan can help against metabolic syndrom.\\

%summary

We have shown that a meal-plan based, digitaly generated shopping lists can have a positive impact on the efficiency of grocery shopping and provide a healthy diet. 
